Guidelines and Policy for Surveys using \SW

### 2014-10-28 doc/sw-publication-policy-gen.tex
minor edits to policy gen

\title{Guidelines and Policy for Surveys using \SW}
\author{Phil Marshall \& Aprajita Verma}
\date{April 15, 2013}
\maketitle

@@

\subsection{Future Project Proposals}
Any future \sw projects are requested to liaise with the \sw PIs regarding their project. We ask that potential project teams first approach the \sw PIs (Marshall, Verma, More collectively contacted via \href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com}) with a short description of their project that includes the following information.

>>>>

\title{Guidelines and Policy for Surveys using \SW}
\author{Phil Marshall, Aprajita Verma \& Anupreeta More}
\date{April 15, 2013}
\maketitle

@@

\subsection{Future Project Proposals}
Any future \sw projects are requested to liaise with the \sw PIs regarding their project. We ask that potential project teams first approach the \sw PIs (Phil Marshall, Anupreeta More, Aprajita Verma, collectively contacted via \href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com}) with a short description of their project that includes the following information.
